## Prompt 6

Now, using the attached (Kaggle Diabetes) dataset, write R code to 

 1. Explore the data
 2. Generate some summary statistics, relevant for machine learning
 3. Assuming the variable 'Outcome' as the prediction class, write R code, using tidymodels to run a logisctic regression model
 4. Using the same outcome, write tidymodels R code for a Random Forest and an XGBoost classification
 5. Run an unsupervised clustering using PCS in tidymodels R syntax.
 GPT

ANSWER
The provided zip file contains a single file named diabetes.csv. This file will be used for the R code tasks you requested, which 
include data exploration, generating summary statistics, 
logistic regression, random forest and XGBoost classification models, as well as unsupervised 
clustering using PCA. Let's write the R code for each of these tasks:

1. Explore the Data

```{r}
library(readr)
library(dplyr)

# Load the dataset
## Note that we replace the local file with the download link to the zip-file for reproducibility reasons
download.file()
# unzip
data <- read_csv('path/to/diabetes.csv')

# View the first few rows of the dataset
head(data)

# View the structure of the dataset
str(data)
```

## 2. Generate Summary Statistics

```{r}
# Summary statistics
summary(data)

# Count of outcomes
table(data$Outcome)
```

