## 3. Logistic Regression Model Using tidymodels

```{r}
library(tidymodels)

# Split the data into training and testing sets
set.seed(123)
data_split <- initial_split(data, prop = 0.8)
train_data <- training(data_split)
test_data <- testing(data_split)

# Define the model using logistic regression
logistic_reg_spec <- logistic_reg() %>% 
  set_engine("glm")

# Define the workflow
logistic_workflow <- workflow() %>% 
  add_model(logistic_reg_spec) %>% 
  add_formula(Outcome ~ .)

# Fit the model
logistic_fit <- logistic_workflow %>% 
  fit(data = train_data)

# Evaluate the model
logistic_results <- logistic_fit %>% 
  predict(test_data) %>% 
  bind_cols(test_data) %>% 
  metrics(truth = Outcome, estimate = .pred_class)
```

## 4. Random Forest and XGBoost Classification

### Random Forest

```{r}
# Random Forest model
random_forest_spec <- rand_forest() %>% 
  set_engine("ranger") %>% 
  set_mode("classification")

# Workflow
random_forest_workflow <- workflow() %>% 
  add_model(random_forest_spec) %>% 
  add_formula(Outcome ~ .)

# Fit the model
random_forest_fit <- random_forest_workflow %>% 
  fit(data = train_data)
```

### XGBoost

```{r}
# XGBoost model
xgboost_spec <- boost_tree() %>% 
  set_engine("xgboost") %>% 
  set_mode("classification")

# Workflow
xgboost_workflow <- workflow() %>% 
  add_model(xgboost_spec) %>% 
  add_formula(Outcome ~ .)

# Fit the model
xgboost_fit <- xgboost_workflow %>% 
  fit(data = train_data)
```

## 5. Unsupervised Clustering Using PCA

```{r}
# Unsupervised clustering using PCA
pca_spec <- recipe(~., data = train_data) %>% 
  step_normalize(all_predictors()) %>% 
  step_pca(all_predictors(), num_comp = 2)

# Preparing the PCA recipe
pca_prep <- prep(pca_spec, training = train_data)

# Applying the PCA
pca_data <- bake(pca_prep, new_data = train_data)

# Exploring the PCA results
head(pca_data)

Note: Replace path/to/diabetes.csv with the actual path to your dataset file. Also, the exact parameters for the 
models (like the number of trees in the random forest, or the number of components in PCA) may need to be tuned based on 
the specific characteristics of 
your dataset. ​
